---
title: "Weekly Resident Review"
format:
  html:
    embed-resources: true
    theme: none
execute:
  echo: false
  warning: false
  message: false
params:
  record_id: NA
  resident_name: "Resident"
  rdm_token: NA
  redcap_url: "https://redcapsurvey.slu.edu/api/"
  digest_app_url: ""
---

```{r setup}
library(httr)
library(jsonlite)
library(dplyr)
library(knitr)
suppressPackageStartupMessages({
  library(gmed)
  library(amiontools)
})
source("R/fetch_resident_digest_data.R")

# Email rendering constraint (see fetch_resident_digest_data.R header): plain
# HTML tables + inline styles only. No plotly/DT/htmlwidgets — Outlook and
# most email clients don't run JavaScript, so an interactive widget would
# render blank or broken for most residents.
d <- build_resident_digest_data(
  record_id      = params$record_id,
  rdm_token      = params$rdm_token,
  redcap_url     = params$redcap_url,
  digest_app_url = params$digest_app_url
)

stat_box <- function(number, label, warn = FALSE) {
  color <- if (warn) "#b8860b" else "#003d5c"
  sprintf(
    '<td style="padding:12px 18px; text-align:center; border:1px solid #e0e0e0;">
       <div style="font-size:1.6rem; font-weight:700; color:%s;">%s</div>
       <div style="font-size:0.75rem; color:#6c757d; margin-top:2px;">%s</div>
     </td>', color, number, label)
}

action_link <- function(url, text) {
  if (is.na(url)) return(sprintf('<p style="color:#6c757d; font-size:0.85rem;">%s (link unavailable — open the resident digest app directly)</p>', text))
  sprintf('<p><a href="%s" style="background:#003d5c; color:#fff; padding:8px 16px; border-radius:4px; text-decoration:none; font-size:0.9rem;">%s &rarr;</a></p>', url, text)
}

# Same live app used by mod_eval_summary.R in imslu.resident.digest — a
# resident shares this link with a supervising faculty member to prompt an
# evaluation. Kept as a literal constant in both places (thin repos, no
# shared package layer between them for a single URL).
RESIDENT_ASSESSMENT_URL <- "https://fbuckhold3-imslu-resident-assessment.share.connect.posit.cloud"
```

<div style="font-family: -apple-system, Segoe UI, Helvetica, Arial, sans-serif; max-width: 640px; margin: 0 auto; color:#212529;">

<h2 style="color:#003d5c;">`r params$resident_name`'s Weekly Resident Review</h2>
<p style="color:#6c757d; font-size:0.85rem;">Week of `r format(Sys.Date(), "%B %d, %Y")`</p>
```{r header-info}
#| results: asis
if (!is.na(d$resident$access_code) || !is.na(d$resident$coach_name)) {
  bits <- c(
    if (!is.na(d$resident$coach_name)) sprintf("Coach: <strong>%s</strong>", d$resident$coach_name),
    if (!is.na(d$resident$access_code)) sprintf("Access code: <strong>%s</strong>", d$resident$access_code)
  )
  cat(sprintf('<p style="color:#6c757d; font-size:0.85rem;">%s</p>', paste(bits, collapse = " &nbsp;&middot;&nbsp; ")))
}
```
<p style="color:#212529; font-size:0.95rem;">As the week wraps up, here's a look at your duty hours, schedule, attendance, and evaluations — with a few quick things worth updating.</p>

## Duty Hours

<table style="border-collapse: collapse; width:100%;"><tr>
```{r duty-stats}
#| results: asis
cat(stat_box(ifelse(is.na(d$duty$this_week_hours), "—", d$duty$this_week_hours), "Hours This Week"))
cat(stat_box(ifelse(is.na(d$duty$rolling_4wk_avg), "—", d$duty$rolling_4wk_avg), "4-Week Avg / Week",
             warn = isTRUE(d$duty$flag_80h)))
```
</tr></table>

```{r duty-flag}
#| results: asis
if (isTRUE(d$duty$flag_80h))
  cat('<p style="color:#b8860b; font-size:0.85rem;">⚠ Your 4-week rolling average is over 80 hours/week. Review your entries and talk to your program if this looks wrong.</p>')
cat(action_link(d$duty$link, "Confirm or Log Duty Hours"))
```

## Your Schedule — Next Week

```{r schedule-table}
#| results: asis
rows <- d$schedule$rows
if (is.null(rows) || nrow(rows) == 0) {
  cat('<p style="color:#6c757d; font-size:0.85rem;">No schedule found for next week yet.</p>')
} else {
  tbl <- rows |>
    transmute(Date = format(Date, "%a %b %d"),
              Rotation = coalesce(as.character(Rotation), ""))
  cat(kable(tbl, format = "html", table.attr = 'style="width:100%; border-collapse:collapse;"',
            row.names = FALSE))
}
```

## Noon Conference Attendance

<table style="border-collapse: collapse; width:100%;"><tr>
```{r attendance-stats}
#| results: asis
cat(stat_box(ifelse(is.na(d$attendance$n_this_week), "—", d$attendance$n_this_week),
             "Logged This Week"))
```
</tr></table>
```{r attendance-link}
#| results: asis
cat(action_link(d$attendance$link, "Review or Add Attendance"))
```

## Evaluations & Feedback

<table style="border-collapse: collapse; width:100%;"><tr>
```{r eval-stats}
#| results: asis
cat(stat_box(ifelse(is.na(d$evals$n_received_week), "—", d$evals$n_received_week),
             "Evaluations Received — Past Week"))
cat(stat_box(ifelse(is.na(d$evals$n_completed_2wk), "—", d$evals$n_completed_2wk),
             "Faculty Evals You've Done — Last 2 Weeks",
             warn = !isTRUE(d$evals$completed_done_this_week)))
```
</tr></table>

```{r eval-nudge}
#| results: asis
if (!isTRUE(d$evals$completed_done_this_week)) {
  cat('<p style="font-size:0.85rem;">Haven\'t evaluated a faculty member this week? A couple minutes of feedback goes a long way.</p>')
  cat(action_link(d$evals$link, "Evaluate a Faculty Member"))
}
if (is.na(d$evals$n_received_week) || d$evals$n_received_week == 0)
  cat('<p style="font-size:0.85rem;">No evaluations received this week — consider asking a supervising faculty member for feedback.</p>')
cat(action_link(RESIDENT_ASSESSMENT_URL, "Share Evaluation Link with a Faculty Member"))
```

## Peer Review

<table style="border-collapse: collapse; width:100%;"><tr>
```{r peer-stats}
#| results: asis
cat(stat_box(ifelse(is.na(d$peer$n_completed_2wk), "—", d$peer$n_completed_2wk),
             "Peer Reviews Done — Last 2 Weeks", warn = !isTRUE(d$peer$done_this_week)))
```
</tr></table>

```{r peer-teammates}
#| results: asis
tm <- d$peer$teammates
if (!is.null(tm) && is.data.frame(tm) && nrow(tm) > 0) {
  names_str <- paste(unique(tm$name), collapse = ", ")
  cat(sprintf('<p style="font-size:0.85rem;">People you\'ve recently worked with (last 4 weeks): %s</p>', names_str))
}
if (!isTRUE(d$peer$done_this_week))
  cat(action_link(d$peer$link, "Review a Peer"))
```

## Scholarship

<p style="font-size:0.9rem;">Presented at noon conference, PCEC, or an afternoon-school session? Log it — every in-program presentation counts.</p>
```{r schol-link}
#| results: asis
cat(action_link(d$scholarship_link, "Add Scholarship"))
```

<hr style="margin: 24px 0; border: none; border-top: 1px solid #e0e0e0;">
<p style="font-size:0.75rem; color:#adb5bd;">
Automated weekly digest — IMSLU Internal Medicine Residency.
</p>

</div>
