---
title: "IMSLU Residency Program Weekly Assessment Report"
format:
  html:
    toc: true
    toc-depth: 2
    theme: cosmo
    embed-resources: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup, message=FALSE, warning=FALSE}
library(httr)
library(dplyr)
library(knitr)
library(ggplot2)
library(htmltools)
library(blastula)

# Source helper functions
source("R/fetch_redcap_data.R")
source("R/utils.R")

# Set ggplot theme for consistent styling
theme_set(theme_minimal(base_size = 16) +
  theme(
    plot.title = element_text(face = "bold", size = 18),
    plot.subtitle = element_text(size = 14, color = "grey40"),
    axis.title = element_text(face = "bold", size = 14),
    axis.text = element_text(size = 12),
    panel.grid.minor = element_blank()
  ))
```

```{r fetch-data}
# Fetch data from both REDCap databases
fac_data <- fetch_faculty_data()
res_data <- fetch_resident_data()

# Calculate time periods
academic_year_start <- get_academic_year_start()
four_weeks_ago <- Sys.Date() - 28

# Calculate key metrics
avg_evals_year <- get_avg_evaluations_per_resident(res_data, academic_year_start)
avg_evals_4wk <- get_avg_evaluations_per_resident(res_data, four_weeks_ago)
avg_conf_year <- get_avg_conferences_per_resident(res_data, academic_year_start)
avg_conf_4wk <- get_avg_conferences_per_resident(res_data, four_weeks_ago)

# Total counts
total_assessments_year <- nrow(res_data[res_data$redcap_repeat_instrument == "Assessment" &
                                        !is.na(res_data$ass_date) &
                                        as.Date(res_data$ass_date) >= academic_year_start, ])
total_assessments_4wk <- nrow(res_data[res_data$redcap_repeat_instrument == "Assessment" &
                                       !is.na(res_data$ass_date) &
                                       as.Date(res_data$ass_date) >= four_weeks_ago, ])

# Get top contributors for callouts
top_fac_4wk <- get_top_faculty(res_data, four_weeks_ago, top_n = 1)
top_res_year <- get_top_residents_fac_eval(res_data, academic_year_start, top_n = 1)
top_res_4wk <- get_top_residents_fac_eval(res_data, four_weeks_ago, top_n = 1)
```

::: {.subject}
IMSLU Weekly Assessment Report - `r format(Sys.Date(), "%B %d, %Y")`
:::

::: {.email}
## Weekly Residency Program Report

This week's assessment report for the IMSLU Residency Program includes:

- **Faculty Assessments**: `r total_assessments_4wk` assessments completed in the last 4 weeks
- **Academic Year Total**: `r total_assessments_year` assessments completed since `r format(academic_year_start, "%B %Y")`

The full detailed report is attached below with charts, tables, and complete metrics.

**Quick Links:**
- [Submit Resident Assessment](https://fbuckhold3-imslu-resident-assessment.share.connect.posit.cloud)
- [Submit Faculty Evaluation](https://fbuckhold3-imslu-facultyeval.share.connect.posit.cloud)
:::

---

## 🔗 Quick Links

📝 [Submit Resident Assessment](https://fbuckhold3-imslu-resident-assessment.share.connect.posit.cloud)

📝 [Submit Faculty Evaluation](https://fbuckhold3-imslu-facultyeval.share.connect.posit.cloud)

📝 [Submit Attendance at Noon Conference](https://fbuckhold3-imslu-at-noon.share.connect.posit.cloud)

---

## Faculty / Fellow Assessment of Residents

Quality assessment and feedback is how residents in the IMSLU Residency Program improve and how the Program makes determinations of competence.

We expect residents obtain at least **25 assessments per year**, with the goal of getting one weekly.

Who in the Department should be giving feedback? Everyone that works with a resident - Faculty or Fellows.

Completing an assessment is simple and can be done with a mobile device and has a voice to text option. Access it [here](https://fbuckhold3-imslu-resident-assessment.share.connect.posit.cloud).

Below is a status report for assessments gathered for the year and in the last 4 weeks. `r if(nrow(top_fac_4wk) > 0 && !is.na(top_fac_4wk$Faculty[1])) paste0("Shout out to **", top_fac_4wk$Faculty[1], "** for being the Faculty Champion of Assessments!")`

### 📊 Key Metrics - Academic Year

*Since `r format(academic_year_start, "%B %d, %Y")`*

```{r metrics-year, results='asis', echo=FALSE}
htmltools::HTML(sprintf('
<div style="display: flex; justify-content: space-around; margin: 20px 0; flex-wrap: wrap;">
  <div style="text-align: center; padding: 20px; background: #f0f9ff; border-radius: 10px; min-width: 200px; margin: 10px;">
    <div style="font-size: 48px; font-weight: bold; color: #0369a1;">%.1f</div>
    <div style="font-size: 14px; color: #64748b;">Avg Evaluations/Resident</div>
  </div>
  <div style="text-align: center; padding: 20px; background: #f0fdf4; border-radius: 10px; min-width: 200px; margin: 10px;">
    <div style="font-size: 48px; font-weight: bold; color: #15803d;">%d</div>
    <div style="font-size: 14px; color: #64748b;">Total Assessments</div>
  </div>
</div>
', avg_evals_year, total_assessments_year))
```

### 📊 Key Metrics - Last 4 Weeks

*Last 28 days*

```{r metrics-4wk, results='asis', echo=FALSE}
htmltools::HTML(sprintf('
<div style="display: flex; justify-content: space-around; margin: 20px 0; flex-wrap: wrap;">
  <div style="text-align: center; padding: 20px; background: #f0f9ff; border-radius: 10px; min-width: 200px; margin: 10px;">
    <div style="font-size: 48px; font-weight: bold; color: #0369a1;">%.1f</div>
    <div style="font-size: 14px; color: #64748b;">Avg Evaluations/Resident</div>
  </div>
  <div style="text-align: center; padding: 20px; background: #f0fdf4; border-radius: 10px; min-width: 200px; margin: 10px;">
    <div style="font-size: 48px; font-weight: bold; color: #15803d;">%d</div>
    <div style="font-size: 14px; color: #64748b;">Total Assessments</div>
  </div>
</div>
', avg_evals_4wk, total_assessments_4wk))
```

### 📈 Assessments by Specialty - Academic Year

```{r specialty-year, fig.width=12, fig.height=8}
year_specialty <- get_assessments_by_specialty_for_plot(res_data, academic_year_start)

if (nrow(year_specialty) > 0) {
  ggplot(year_specialty, aes(x = reorder(Specialty, Count), y = Count, fill = Count)) +
    geom_col() +
    geom_text(aes(label = Count), hjust = -0.2, size = 5, fontface = "bold") +
    coord_flip() +
    scale_fill_gradient(low = "#93c5fd", high = "#1e3a8a") +
    labs(
      title = "Assessments by Specialty",
      subtitle = paste("Academic Year:", format(academic_year_start, "%b %Y"), "- Present"),
      x = NULL,
      y = "Number of Assessments"
    ) +
    theme(legend.position = "none") +
    expand_limits(y = max(year_specialty$Count) * 1.15)
} else {
  plot.new()
  text(0.5, 0.5, "No assessment data available", cex = 1.5, col = "gray50")
}
```

### 📈 Assessments by Specialty - Last 4 Weeks

```{r specialty-4wk, fig.width=12, fig.height=8}
fourwk_specialty <- get_assessments_by_specialty_for_plot(res_data, four_weeks_ago)

if (nrow(fourwk_specialty) > 0) {
  ggplot(fourwk_specialty, aes(x = reorder(Specialty, Count), y = Count, fill = Count)) +
    geom_col() +
    geom_text(aes(label = Count), hjust = -0.2, size = 5, fontface = "bold") +
    coord_flip() +
    scale_fill_gradient(low = "#86efac", high = "#166534") +
    labs(
      title = "Assessments by Specialty",
      subtitle = "Last 4 Weeks",
      x = NULL,
      y = "Number of Assessments"
    ) +
    theme(legend.position = "none") +
    expand_limits(y = max(fourwk_specialty$Count) * 1.15)
} else {
  plot.new()
  text(0.5, 0.5, "No assessment data available", cex = 1.5, col = "gray50")
}
```

### 🎉 Top Faculty Contributors - Academic Year

```{r top-faculty-year}
top_fac_year <- get_top_faculty(res_data, academic_year_start, top_n = 5)
kable(top_fac_year, align = c('l', 'r'))
```

### 🎉 Top Faculty Contributors - Last 4 Weeks

```{r top-faculty-4wk}
top_fac_4wk_full <- get_top_faculty(res_data, four_weeks_ago, top_n = 5)
kable(top_fac_4wk_full, align = c('l', 'r'))
```

---

## Conference Attendance

The IMSLU Program has started to track Noon Conference Attendance. This is an expectation of ALL residents to attend - if on the SSM Campus to go to the SLU Hospital Conference, if at VA then the VA.

Below is the breakdown by rotation of Conference Attendance.

### 📊 Attendance Metrics - Academic Year

*Since `r format(academic_year_start, "%B %d, %Y")`*

```{r conf-metrics-year, results='asis', echo=FALSE}
htmltools::HTML(sprintf('
<div style="display: flex; justify-content: space-around; margin: 20px 0; flex-wrap: wrap;">
  <div style="text-align: center; padding: 20px; background: #fef3c7; border-radius: 10px; min-width: 200px; margin: 10px;">
    <div style="font-size: 48px; font-weight: bold; color: #b45309;">%.1f</div>
    <div style="font-size: 14px; color: #64748b;">Avg Attendance/Resident</div>
  </div>
</div>
', avg_conf_year))
```

### 📊 Attendance Metrics - Last 4 Weeks

*Last 28 days*

```{r conf-metrics-4wk, results='asis', echo=FALSE}
htmltools::HTML(sprintf('
<div style="display: flex; justify-content: space-around; margin: 20px 0; flex-wrap: wrap;">
  <div style="text-align: center; padding: 20px; background: #fef3c7; border-radius: 10px; min-width: 200px; margin: 10px;">
    <div style="font-size: 48px; font-weight: bold; color: #b45309;">%.1f</div>
    <div style="font-size: 14px; color: #64748b;">Avg Attendance/Resident</div>
  </div>
</div>
', avg_conf_4wk))
```

### 📈 Attendance by Rotation - Academic Year

```{r attendance-year, fig.width=12, fig.height=8}
q_year <- count_questions_by_rotation(res_data, academic_year_start)

if (nrow(q_year) > 0) {
  ggplot(q_year, aes(x = reorder(Rotation, `Question Count`), y = `Question Count`, fill = `Question Count`)) +
    geom_col() +
    geom_text(aes(label = `Question Count`), hjust = -0.2, size = 5, fontface = "bold") +
    coord_flip() +
    scale_fill_gradient(low = "#fde68a", high = "#92400e") +
    labs(
      title = "Conference Attendance by Rotation",
      subtitle = paste("Academic Year:", format(academic_year_start, "%b %Y"), "- Present"),
      x = NULL,
      y = "Number of Attendances"
    ) +
    theme(legend.position = "none") +
    expand_limits(y = max(q_year$`Question Count`) * 1.15)
} else {
  plot.new()
  text(0.5, 0.5, "No attendance data available", cex = 1.5, col = "gray50")
}
```

### 📈 Attendance by Rotation - Last 4 Weeks

```{r attendance-4wk, fig.width=12, fig.height=8}
q_4wk <- count_questions_by_rotation(res_data, four_weeks_ago)

if (nrow(q_4wk) > 0) {
  ggplot(q_4wk, aes(x = reorder(Rotation, `Question Count`), y = `Question Count`, fill = `Question Count`)) +
    geom_col() +
    geom_text(aes(label = `Question Count`), hjust = -0.2, size = 5, fontface = "bold") +
    coord_flip() +
    scale_fill_gradient(low = "#fde68a", high = "#92400e") +
    labs(
      title = "Conference Attendance by Rotation",
      subtitle = "Last 4 Weeks",
      x = NULL,
      y = "Number of Attendances"
    ) +
    theme(legend.position = "none") +
    expand_limits(y = max(q_4wk$`Question Count`) * 1.15)
} else {
  plot.new()
  text(0.5, 0.5, "No attendance data available", cex = 1.5, col = "gray50")
}
```

---

## Resident Evaluation of Faculty

Residents are expected to complete 25 evaluations of faculty each year. `r if(nrow(top_res_year) > 0 && !is.na(top_res_year$Resident[1])) paste0("Shout out to **", top_res_year$Resident[1], "** for doing so many")``r if(nrow(top_res_4wk) > 0 && !is.na(top_res_4wk$Resident[1])) paste0(", and congratulations to **", top_res_4wk$Resident[1], "** for being the leader of the last 4 weeks!")`

Faculty assessment can be done [here](https://fbuckhold3-imslu-facultyeval.share.connect.posit.cloud).

### 🏆 Top Residents - Faculty Evaluations - Academic Year

```{r top-res-year-table}
top_res_year_full <- get_top_residents_fac_eval(res_data, academic_year_start, top_n = 5)
kable(top_res_year_full, align = c('l', 'r'))
```

### 🏆 Top Residents - Faculty Evaluations - Last 4 Weeks

```{r top-res-4wk-table}
top_res_4wk_full <- get_top_residents_fac_eval(res_data, four_weeks_ago, top_n = 5)
kable(top_res_4wk_full, align = c('l', 'r'))
```

---

<div style="text-align: center; color: #64748b; font-size: 12px; margin-top: 40px;">
*Report generated on: `r format(Sys.Date(), "%B %d, %Y")`*

*Academic Year: `r format(academic_year_start, "%Y")` - `r format(academic_year_start + 364, "%Y")`*

*Questions or issues? Contact your program administrator.*
</div>

```{r send-email, include=FALSE}
# Send email using blastula (only when running on Posit Connect)
if (Sys.getenv("RSTUDIO_PRODUCT") == "CONNECT") {

  # For testing: single recipient
  # For production: use get_email_list() to get all faculty and residents
  email_recipients <- "Fred.buckhold@slucare.ssmhealth.com"

  # Uncomment this line for production to email all faculty and residents:
  # source("R/get_email_list.R")
  # email_recipients <- get_email_list()

  # Create email body from the {.email} block content
  email_body <- md(sprintf("
## Weekly Residency Program Report

This week's assessment report for the IMSLU Residency Program includes:

- **Faculty Assessments**: %d assessments completed in the last 4 weeks
- **Academic Year Total**: %d assessments completed since %s

The full detailed report is attached.

**Quick Links:**
- [Submit Resident Assessment](https://fbuckhold3-imslu-resident-assessment.share.connect.posit.cloud)
- [Submit Faculty Evaluation](https://fbuckhold3-imslu-facultyeval.share.connect.posit.cloud)
- [Submit Attendance at Noon Conference](https://fbuckhold3-imslu-at-noon.share.connect.posit.cloud)

---

*Report generated on: %s*
",
    total_assessments_4wk,
    total_assessments_year,
    format(academic_year_start, "%B %Y"),
    format(Sys.Date(), "%B %d, %Y")
  ))

  # Create email
  email <- compose_email(body = email_body)

  # Attach the rendered HTML report
  email <- add_attachment(
    email,
    file = "weekly_report.html"
  )

  # Send email via Posit Connect's email service
  email %>%
    smtp_send(
      to = email_recipients,
      from = "noreply@posit.cloud",
      subject = sprintf("IMSLU Weekly Assessment Report - %s", format(Sys.Date(), "%B %d, %Y")),
      credentials = connect_credentials()
    )
}
```
