---
title: "Weekly Resident Evaluation Report"
format:
  html:
    toc: true
    toc-depth: 2
    theme: default
    embed-resources: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(httr)
library(dplyr)
library(knitr)
library(ggplot2)

# Source helper functions
source("R/fetch_redcap_data.R")
source("R/utils.R")
```

```{r fetch-data}
# Fetch data from both REDCap databases
fac_data <- fetch_faculty_data()
res_data <- fetch_resident_data()

# Calculate time periods
academic_year_start <- get_academic_year_start()
four_weeks_ago <- Sys.Date() - 28
```

```{r email-recipients, include=FALSE}
#' Get email recipients from faculty and resident databases
#' This function is used by Posit Connect for email distribution
get_email_recipients <- function() {
  # Fetch fresh data for email addresses
  fac_data <- fetch_faculty_data()
  res_data <- fetch_resident_data()

  # Extract faculty emails
  fac_emails <- character(0)
  if (nrow(fac_data) > 0 && "fac_email" %in% names(fac_data)) {
    fac_emails <- fac_data$fac_email[!is.na(fac_data$fac_email) & fac_data$fac_email != ""]
  }

  # Extract resident emails (from unique residents, not repeating instances)
  res_emails <- character(0)
  if (nrow(res_data) > 0 && "email" %in% names(res_data)) {
    # Get unique resident records (redcap_repeat_instrument is empty for main records)
    resident_records <- res_data[is.na(res_data$redcap_repeat_instrument) |
                                  res_data$redcap_repeat_instrument == "", , drop = FALSE]
    res_emails <- resident_records$email[!is.na(resident_records$email) &
                                          resident_records$email != ""]
    res_emails <- unique(res_emails)
  }

  # Combine and deduplicate
  all_emails <- unique(c(fac_emails, res_emails))

  # Return as comma-separated string for Posit Connect
  paste(all_emails, collapse = ", ")
}

# Store email list for reference
email_recipients <- get_email_recipients()
```

## Summary

This report provides evaluation metrics for the current academic year (`r format(academic_year_start, "%B %d, %Y")` to `r format(academic_year_start + 364, "%B %d, %Y")`) and the last 4 weeks.

**Data Source:** REDCap RDM and Faculty databases
**Active Residents Only** (archived residents excluded)

---

## Assessment Evaluations by Faculty

Assessments are categorized by type based on the fields completed:

- **Continuity Clinic** - Longitudinal clinic assessments
- **Clinic Day** - Single clinic session assessments
- **Consults** - Consultation service assessments
- **Intern Inpatient** - Inpatient intern assessments
- **Resident Inpatient** - Inpatient senior resident assessments
- **Observational** - Direct observation assessments

### Academic Year To Date

#### Total by Assessment Type

```{r assess-year-total}
year_totals <- count_assessments_by_type(res_data, academic_year_start)
if (nrow(year_totals) > 0) {
  kable(year_totals)
} else {
  cat("*No assessment data available for this period.*\n")
}
```

#### By Type and Specialty

```{r assess-year-detail}
year_detail <- count_assessments_by_type_specialty(res_data, academic_year_start, "Count")
if (nrow(year_detail) > 0) {
  kable(year_detail)
} else {
  cat("*No assessment data available for this period.*\n")
}
```

### Last 4 Weeks

#### Total by Assessment Type

```{r assess-4wk-total}
fourwk_totals <- count_assessments_by_type(res_data, four_weeks_ago)
if (nrow(fourwk_totals) > 0) {
  kable(fourwk_totals)
} else {
  cat("*No assessment data available for this period.*\n")
}
```

#### By Type and Specialty

```{r assess-4wk-detail}
fourwk_detail <- count_assessments_by_type_specialty(res_data, four_weeks_ago, "Count")
if (nrow(fourwk_detail) > 0) {
  kable(fourwk_detail)
} else {
  cat("*No assessment data available for this period.*\n")
}
```

---

## 🎉 Shout-Outs: Top Faculty

### Academic Year Champions

```{r top-faculty-year}
top_fac_year <- get_top_faculty(res_data, academic_year_start, top_n = 5)
if (nrow(top_fac_year) > 0) {
  kable(top_fac_year)
} else {
  cat("*No faculty evaluation data available for this period.*\n")
}
```

### Last 4 Weeks MVP

```{r top-faculty-4wk}
top_fac_4wk <- get_top_faculty(res_data, four_weeks_ago, top_n = 5)
if (nrow(top_fac_4wk) > 0) {
  kable(top_fac_4wk)
} else {
  cat("*No faculty evaluation data available for this period.*\n")
}
```

---

## Faculty Evaluations by Residents

Residents evaluate faculty after working with them on rotations.

### 🎉 Shout-Outs: Top Residents

#### Academic Year Champions

```{r top-res-year}
top_res_year <- get_top_residents_fac_eval(res_data, academic_year_start, top_n = 5)
if (nrow(top_res_year) > 0) {
  kable(top_res_year)
} else {
  cat("*No resident evaluation data available for this period.*\n")
}
```

#### Last 4 Weeks MVP

```{r top-res-4wk}
top_res_4wk <- get_top_residents_fac_eval(res_data, four_weeks_ago, top_n = 5)
if (nrow(top_res_4wk) > 0) {
  kable(top_res_4wk)
} else {
  cat("*No resident evaluation data available for this period.*\n")
}
```

---

## Questions Submitted by Rotation

Residents submit questions during rotations for noon conference discussions.

### Academic Year

```{r questions-year}
q_year <- count_questions_by_rotation(res_data, academic_year_start)
if (nrow(q_year) > 0) {
  kable(q_year)
} else {
  cat("*No questions submitted for this period.*\n")
}
```

### Last 4 Weeks

```{r questions-4wk}
q_4wk <- count_questions_by_rotation(res_data, four_weeks_ago)
if (nrow(q_4wk) > 0) {
  kable(q_4wk)
} else {
  cat("*No questions submitted for this period.*\n")
}
```

---

## Quick Links

### For Faculty

📝 [Submit Resident Assessment](https://fbuckhold3-imslu-resident-assessment.share.connect.posit.cloud)

### For Residents

📝 [Submit Faculty Evaluation](https://fbuckhold3-imslu-facultyeval.share.connect.posit.cloud)
📝 [Submit Attendance at Noon Conference](https://fbuckhold3-imslu-at-noon.share.connect.posit.cloud)

### For Administrators

📊 [View RDM Database](https://redcapsurvey.slu.edu/)
📊 [View Faculty Database](https://redcapsurvey.slu.edu/)

---

*Report generated on: `r format(Sys.Date(), "%B %d, %Y")`*
*Academic Year: `r format(academic_year_start, "%Y")` - `r format(academic_year_start + 364, "%Y")`*

*Questions or issues? Contact your program administrator.*
