---
title: "Weekly Faculty Evaluation & Attendance Report"
format:
  html:
    toc: false
    theme: default
    embed-resources: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(httr)
library(dplyr)
library(knitr)
library(ggplot2)

# Source helper functions
source("R/fetch_redcap_data.R")
source("R/utils.R")
```

```{r fetch-data}
# Fetch data from both REDCap databases
fac_data <- fetch_faculty_data()
res_data <- fetch_resident_data()
```

## Summary

This report provides a weekly summary of resident evaluation collection and faculty evaluation completion, broken down by specialty, provider, and resident.

**Data pulled from:** REDCap RDM and Faculty databases
**Active residents only** (archived residents excluded)

---

### Assessment Evaluations Collected

Assessment evaluations are completed by faculty for residents rotating through various specialties.

#### By Specialty

```{r evals-by-specialty}
specialty_counts <- count_by_specialty(res_data)
kable(specialty_counts)
```

#### By Faculty Provider

```{r evals-by-provider}
provider_counts <- count_by_provider(res_data)
kable(provider_counts)
```

#### By Resident

```{r evals-by-resident}
resident_counts <- count_by_resident(res_data)
kable(resident_counts)
```

---

### Faculty Evaluations Completed by Residents

Faculty evaluations are completed by residents to evaluate the faculty they worked with during rotations.

```{r faculty-evals}
fac_eval_counts <- count_faculty_evals(res_data)
kable(fac_eval_counts)
```

---

### Quick Links

**For Faculty to Submit Evaluations:**

- [Submit Resident Assessment](https://redcapsurvey.slu.edu/) *(TODO: Add specific REDCap survey link)*

**For Residents:**

- [Submit Faculty Evaluation](https://redcapsurvey.slu.edu/) *(TODO: Add specific REDCap survey link)*

**For Administrators:**

- [View RDM Database](https://redcapsurvey.slu.edu/) *(TODO: Add specific project link)*
- [View Faculty Database](https://redcapsurvey.slu.edu/) *(TODO: Add specific project link)*

---

*Report generated on: `r format(Sys.Date(), "%B %d, %Y")`*

*Questions or issues? Contact your program administrator.*
