---
title: "Weekly Resident Evaluation Report"
format:
  html:
    toc: true
    toc-depth: 2
    theme: cosmo
    embed-resources: true
execute:
  echo: false
  warning: true
  message: false
---

```{r setup}
library(httr)
library(dplyr)
library(knitr)
library(ggplot2)

# Source helper functions
source("R/fetch_redcap_data.R")
source("R/utils.R")

# Set ggplot theme for consistent styling
theme_set(theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(size = 12, color = "grey40"),
    axis.title = element_text(face = "bold"),
    panel.grid.minor = element_blank()
  ))
```

```{r fetch-data}
# Fetch data from both REDCap databases
fac_data <- fetch_faculty_data()
res_data <- fetch_resident_data()

# Calculate time periods
academic_year_start <- get_academic_year_start()
four_weeks_ago <- Sys.Date() - 28

# Calculate key metrics
avg_evals_year <- get_avg_evaluations_per_resident(res_data, academic_year_start)
avg_evals_4wk <- get_avg_evaluations_per_resident(res_data, four_weeks_ago)
avg_conf_year <- get_avg_conferences_per_resident(res_data, academic_year_start)
avg_conf_4wk <- get_avg_conferences_per_resident(res_data, four_weeks_ago)

# Total counts
total_assessments_year <- nrow(res_data[res_data$redcap_repeat_instrument == "Assessment" &
                                        !is.na(res_data$ass_date) &
                                        as.Date(res_data$ass_date) >= academic_year_start, ])
total_assessments_4wk <- nrow(res_data[res_data$redcap_repeat_instrument == "Assessment" &
                                       !is.na(res_data$ass_date) &
                                       as.Date(res_data$ass_date) >= four_weeks_ago, ])
```

## 📊 Key Metrics

::: {.panel-tabset}

### Academic Year

<div style="display: flex; justify-content: space-around; margin: 20px 0;">
  <div style="text-align: center; padding: 20px; background: #f0f9ff; border-radius: 10px; min-width: 200px;">
    <div style="font-size: 48px; font-weight: bold; color: #0369a1;">`r round(avg_evals_year, 1)`</div>
    <div style="font-size: 14px; color: #64748b;">Avg Evaluations/Resident</div>
  </div>
  <div style="text-align: center; padding: 20px; background: #f0fdf4; border-radius: 10px; min-width: 200px;">
    <div style="font-size: 48px; font-weight: bold; color: #15803d;">`r total_assessments_year`</div>
    <div style="font-size: 14px; color: #64748b;">Total Assessments</div>
  </div>
  <div style="text-align: center; padding: 20px; background: #fef3c7; border-radius: 10px; min-width: 200px;">
    <div style="font-size: 48px; font-weight: bold; color: #b45309;">`r round(avg_conf_year, 1)`</div>
    <div style="font-size: 14px; color: #64748b;">Avg Conferences/Resident</div>
  </div>
</div>

*Since `r format(academic_year_start, "%B %d, %Y")`*

### Last 4 Weeks

<div style="display: flex; justify-content: space-around; margin: 20px 0;">
  <div style="text-align: center; padding: 20px; background: #f0f9ff; border-radius: 10px; min-width: 200px;">
    <div style="font-size: 48px; font-weight: bold; color: #0369a1;">`r round(avg_evals_4wk, 1)`</div>
    <div style="font-size: 14px; color: #64748b;">Avg Evaluations/Resident</div>
  </div>
  <div style="text-align: center; padding: 20px; background: #f0fdf4; border-radius: 10px; min-width: 200px;">
    <div style="font-size: 48px; font-weight: bold; color: #15803d;">`r total_assessments_4wk`</div>
    <div style="font-size: 14px; color: #64748b;">Total Assessments</div>
  </div>
  <div style="text-align: center; padding: 20px; background: #fef3c7; border-radius: 10px; min-width: 200px;">
    <div style="font-size: 48px; font-weight: bold; color: #b45309;">`r round(avg_conf_4wk, 1)`</div>
    <div style="font-size: 14px; color: #64748b;">Avg Conferences/Resident</div>
  </div>
</div>

*Last 28 days*

:::

---

## 📈 Assessments by Specialty

::: {.panel-tabset}

### Academic Year

```{r specialty-year, fig.width=10, fig.height=6}
year_specialty <- get_assessments_by_specialty_for_plot(res_data, academic_year_start)

if (nrow(year_specialty) > 0) {
  ggplot(year_specialty, aes(x = reorder(Specialty, Count), y = Count, fill = Count)) +
    geom_col() +
    geom_text(aes(label = Count), hjust = -0.2, size = 4) +
    coord_flip() +
    scale_fill_gradient(low = "#93c5fd", high = "#1e40af") +
    labs(
      title = "Assessments by Specialty",
      subtitle = paste("Academic Year:", format(academic_year_start, "%b %Y"), "- Present"),
      x = NULL,
      y = "Number of Assessments"
    ) +
    theme(legend.position = "none") +
    expand_limits(y = max(year_specialty$Count) * 1.1)
} else {
  plot.new()
  text(0.5, 0.5, "No assessment data available", cex = 1.5, col = "gray50")
}
```

### Last 4 Weeks

```{r specialty-4wk, fig.width=10, fig.height=6}
fourwk_specialty <- get_assessments_by_specialty_for_plot(res_data, four_weeks_ago)

if (nrow(fourwk_specialty) > 0) {
  ggplot(fourwk_specialty, aes(x = reorder(Specialty, Count), y = Count, fill = Count)) +
    geom_col() +
    geom_text(aes(label = Count), hjust = -0.2, size = 4) +
    coord_flip() +
    scale_fill_gradient(low = "#86efac", high = "#15803d") +
    labs(
      title = "Assessments by Specialty",
      subtitle = "Last 4 Weeks",
      x = NULL,
      y = "Number of Assessments"
    ) +
    theme(legend.position = "none") +
    expand_limits(y = max(fourwk_specialty$Count) * 1.1)
} else {
  plot.new()
  text(0.5, 0.5, "No assessment data available", cex = 1.5, col = "gray50")
}
```

:::

---

## 🎉 Top Faculty Contributors

::: {.panel-tabset}

### Academic Year Champions

```{r top-faculty-year}
top_fac_year <- get_top_faculty(res_data, academic_year_start, top_n = 5)
kable(top_fac_year, align = c('l', 'r'))
```

### Last 4 Weeks MVP

```{r top-faculty-4wk}
top_fac_4wk <- get_top_faculty(res_data, four_weeks_ago, top_n = 5)
kable(top_fac_4wk, align = c('l', 'r'))
```

:::

---

## 🏆 Top Residents - Faculty Evaluations

::: {.panel-tabset}

### Academic Year Champions

```{r top-res-year}
top_res_year <- get_top_residents_fac_eval(res_data, academic_year_start, top_n = 5)
kable(top_res_year, align = c('l', 'r'))
```

### Last 4 Weeks MVP

```{r top-res-4wk}
top_res_4wk <- get_top_residents_fac_eval(res_data, four_weeks_ago, top_n = 5)
kable(top_res_4wk, align = c('l', 'r'))
```

:::

---

## 💬 Questions by Rotation

::: {.panel-tabset}

### Academic Year

```{r questions-year, fig.width=10, fig.height=6}
q_year <- count_questions_by_rotation(res_data, academic_year_start)

if (nrow(q_year) > 0) {
  ggplot(q_year, aes(x = reorder(Rotation, `Question Count`), y = `Question Count`, fill = `Question Count`)) +
    geom_col() +
    geom_text(aes(label = `Question Count`), hjust = -0.2, size = 4) +
    coord_flip() +
    scale_fill_gradient(low = "#fde68a", high = "#b45309") +
    labs(
      title = "Questions Submitted by Rotation",
      subtitle = paste("Academic Year:", format(academic_year_start, "%b %Y"), "- Present"),
      x = NULL,
      y = "Number of Questions"
    ) +
    theme(legend.position = "none") +
    expand_limits(y = max(q_year$`Question Count`) * 1.1)
} else {
  plot.new()
  text(0.5, 0.5, "No question data available", cex = 1.5, col = "gray50")
}
```

### Last 4 Weeks

```{r questions-4wk, fig.width=10, fig.height=6}
q_4wk <- count_questions_by_rotation(res_data, four_weeks_ago)

if (nrow(q_4wk) > 0) {
  ggplot(q_4wk, aes(x = reorder(Rotation, `Question Count`), y = `Question Count`, fill = `Question Count`)) +
    geom_col() +
    geom_text(aes(label = `Question Count`), hjust = -0.2, size = 4) +
    coord_flip() +
    scale_fill_gradient(low = "#fde68a", high = "#b45309") +
    labs(
      title = "Questions Submitted by Rotation",
      subtitle = "Last 4 Weeks",
      x = NULL,
      y = "Number of Questions"
    ) +
    theme(legend.position = "none") +
    expand_limits(y = max(q_4wk$`Question Count`) * 1.1)
} else {
  plot.new()
  text(0.5, 0.5, "No question data available", cex = 1.5, col = "gray50")
}
```

:::

---

## 🔗 Quick Links

### For Faculty

📝 [Submit Resident Assessment](https://fbuckhold3-imslu-resident-assessment.share.connect.posit.cloud)

### For Residents

📝 [Submit Faculty Evaluation](https://fbuckhold3-imslu-facultyeval.share.connect.posit.cloud)

📝 [Submit Attendance at Noon Conference](https://fbuckhold3-imslu-at-noon.share.connect.posit.cloud)

### For Administrators

📊 [View RDM Database](https://redcapsurvey.slu.edu/)

📊 [View Faculty Database](https://redcapsurvey.slu.edu/)

---

<div style="text-align: center; color: #64748b; font-size: 12px; margin-top: 40px;">
*Report generated on: `r format(Sys.Date(), "%B %d, %Y")`*

*Academic Year: `r format(academic_year_start, "%Y")` - `r format(academic_year_start + 364, "%Y")`*

*Questions or issues? Contact your program administrator.*
</div>
