---
title: "Weekly Faculty Evaluation & Attendance Report"
format:
  html:
    toc: false
    theme: default
    embed-resources: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(httr)
library(dplyr)
library(knitr)
library(ggplot2)

# Source helper functions
source("R/fetch_redcap_data.R")
source("R/utils.R")
```

```{r fetch-data}
# Fetch data from both REDCap databases
fac_data <- fetch_faculty_data()
res_data <- fetch_resident_data()
```

## Summary

This report provides a weekly summary of evaluation collection and attendance tracking broken down by specialty, provider, and resident.

---

### Evaluations Collected

#### By Specialty

```{r evals-by-specialty}
# TODO: Customize based on your actual data structure
# specialty_counts <- count_by_specialty(res_data)
# kable(specialty_counts)

# Placeholder table
kable(data.frame(
  Specialty = c("Example 1", "Example 2"),
  Evaluations = c(0, 0)
))
```

#### By Provider

```{r evals-by-provider}
# TODO: Customize based on your actual data structure
# provider_counts <- count_by_provider(res_data)
# kable(provider_counts)

# Placeholder table
kable(data.frame(
  Provider = c("Example Provider"),
  Evaluations = c(0)
))
```

#### By Resident

```{r evals-by-resident}
# TODO: Customize based on your actual data structure
# resident_counts <- count_by_resident(res_data)
# kable(resident_counts)

# Placeholder table
kable(data.frame(
  Resident = c("Example Resident"),
  Evaluations = c(0)
))
```

---

### Attendance Records

```{r attendance}
# TODO: Customize based on your actual data structure
# attendance_counts <- count_attendance(res_data)
# kable(attendance_counts)

# Placeholder table
kable(data.frame(
  Category = c("Example Category"),
  Count = c(0)
))
```

---

### Quick Links

**For Faculty:**

- [Submit Evaluation](https://redcapsurvey.slu.edu/)
- [Record Attendance](https://redcapsurvey.slu.edu/)

**For Administrators:**

- [View All Evaluations](https://redcapsurvey.slu.edu/)
- [Manage Faculty](https://redcapsurvey.slu.edu/)

---

*Report generated on: `r format(Sys.Date(), "%B %d, %Y")`*
